### 2020-01-15 article_draft.tex
Updates from Overleaf

To achieve this, first define $\Gamma_{1, \distv}(x), \dots, \Gamma_{p, \distv}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\distv(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gamma^*_\distv(x) = \max\left\{\Gamma_{1, \distv}(x), \Gamma_{2, \distv}(x), \dots, \Gamma_{p, \distv}(x)\right\}.
\end{align*}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

@@

\sh{\subsection{Unbiasedness at local alternatives}
Consider a local alternative in which the true value of $\psi$ is shrinking towards zero at a root $n$ rate: $\psi = \underline{h}/\sqrt{n}$.  For each potential norm, we assume the norm is convex.  This assumption can be relaxed to what was described by Eaton and Perlman (1991) (Concentration inequalitites for multivariate distributions: mv normal).  Under this local alternative, we will have $\sqrt{n} \hat{\psi} \xrightarrow{d} N(\underline{h}, \Sigma)$.    
Show that the test will reject the null with a probability greater than $\alpha$ for an $\alpha$ level test}

@@

\begin{lemma}
	\begin{align*}
	\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\distv}(\distv) \text{ and } F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\distv}(\distv)}(\alpha)
	\end{align*}
\end{lemma}
\textcolor{blue}{
	The proofs of these will be similar, but I am not sure quite how to do it.  While the following expansion is useful for me, I am not sure how to deal with each part:
	\begin{align*}
		Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) & = Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) - \left( Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) \right)	
	\end{align*}
	We can make arguments that the second two terms will cancel because of an assumed continuity of our function $\Gamma^*$ with respect to $Q$.  We can also think of $\Gamma^*$ as being indexed by $Q$'s covariance matrix instead of its entire distribution to make more simple continuity arguments.\\
	However, I am not exactly sure how to argue that the first two terms cancel.  Initially I want to use the continuous mapping theorem.  Because the function itself changes with $n$ and is random, I am not sure what to do.  If we again use the continuity of $\Gamma$ could we argue that the values of the random functions will be close to the values of the non-random funcitons (where $\hat\distv$ is replaced by $\distv$)\\
	My other idea was to assume that the function class of $\Gamma*$ is $P$-Donsker, but I think this may be overly complicated, and not necessary.
}

@@

For now, we will assume that each of our $\Gamma_Q(x)$ is a unimodal, centrally symmetric function.  In certain cases, $\Gamma_Q(x)$ is increasing $x$ moves away from the origin. In these cases, for the purposes of this proof, instead use $\Gamma^{-1}_Q(x) = \left(\Gamma_Q(x)\right)^{-1}$.

\begin{lemma}
	\label{lemma:min_cent_sym_unm}
	Let $\Gamma_1(x), \dots, \Gamma_d(x)$ all be centrally symmetric, unimodal functions.  Then $\Gamma^*(x) = \min\left\{\Gamma_1(x), \dots, \Gamma_d(x)\right\}$ is also centrally symmetric and unimodal.

>>>>

To achieve this, first define $\Gamma_{1, \distv}(x), \dots, \Gamma_{p, \distv}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\distv(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gamma^*_\distv(x) = \max\left\{\Gamma_{1, \distv}(x), \Gamma_{2, \distv}(x), \dots, \Gamma_{p, \distv}(x)\right\}.
\end{align*}
\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

@@

\sh{\subsection{Unbiasedness at local alternatives}
Consider a local alternative in which the true value of $\psi$ is shrinking towards zero at a root $n$ rate: $\psi = \underline{h}/\sqrt{n}$.  We assume that each potential norm is convex.  This assumption can be relaxed to what was described by Eaton and Perlman (1991) (Concentration inequalitites for multivariate distributions: mv normal).  Under this local alternative, we will have $\sqrt{n} \hat{\psi} \xrightarrow{d} N(\underline{h}, \Sigma)$.    
Show that the test will reject the null with a probability greater than $\alpha$ for an $\alpha$ level test}

@@

\begin{lemma} \textcolor{red}{plus $h$?}
	\begin{align*}
	\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\distv}(\rvv) \text{ and } F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\distv}(\rvv) }(\alpha)
	\end{align*}
\end{lemma}
\textcolor{blue}{
	The proofs of these will be similar, but I am not sure quite how to do it.  While the following expansion is useful for me, I am not sure how to deal with each part:
	\begin{align*}
		Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) & = Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) - \left( Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) \right)	
	\end{align*}
	We can make arguments that the second two terms will cancel because of an assumed continuity of our function $\Gamma^*$ with respect to $Q$.  We can also think of $\Gamma^*$ as being indexed by $Q$'s covariance matrix instead of its entire distribution to make more simple continuity arguments.\\
	However, I am not exactly sure how to argue that the first two terms cancel.  Initially I want to use the continuous mapping theorem.  Because the function itself changes with $n$ and is random, I am not sure what to do.  If we again use the continuity of $\Gamma$ could we argue that the values of the random functions will be close to the values of the non-random funcitons (where $\hat\distv$ is replaced by $\distv$)\\
	My other idea was to assume that the function class of $\Gamma*$ is $P$-Donsker, but I think this may be overly complicated, and not necessary.
}

@@

For now, we will assume that each of our $\Gamma_Q$ is a unimodal, centrally symmetric function.  In certain cases, $\Gamma_Q$ is increasing $x$ moves away from the origin. In these cases, for the purposes of this proof, instead use $\Gamma^{-1}_Q(x) = \left(\Gamma_Q(x)\right)^{-1}$.

\begin{lemma}
	\label{lemma:min_cent_sym_unm}
	Let $\Gamma_1, \dots, \Gamma_d$ all be centrally symmetric, unimodal functions.  Then $\Gamma^* = \min\left\{\Gamma_1, \dots, \Gamma_d\right\}$ is also centrally symmetric and unimodal.
